Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-09-07 Manuscript/manuscript.tex
MS: minor update

\begin{figure}[]
  \centering
  \includegraphics[height=9.0cm,angle=-90]{../Fig/bound-CAs_conc-eccl17.eps}
  \caption{\label{fig:cacl-bind}
    Binding isotherm assuming stoichiometry of 2~POPC:1~\ce{Ca^{2+}} as used in \cite{altenbach84} fits our simulation data well .
    }
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=6.0cm]{../Fig/volmap_resid10_Ca_Cl_PO4Cent.png} \\
  \includegraphics[width=4.0cm]{../Fig/volmap_resid10_Ca_Cl_sn1Cent.png}
  \includegraphics[width=3.6cm]{../Fig/volmap_resid10_Ca_Cl_sn2Cent.png}
  \caption{\label{fig:volmaps}
      Contours of probability isodensities of \ce{Ca2+} with respect to 
      various moieties fixed in space (highlighted with transparent spheres): 
      phosphate moiety, side chain 1 carbonyl group and side chain 2 carbonyl group.
      Shown contours suggest that the dominant contribution 
      to \ce{Ca2+} binding likely comes from the phosphate group, 
      but remain inconclusive on the details of the interactions with any of the two carbonyl groups. 
  }
\end{figure}

>>>>

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=6.0cm]{../Fig/volmap_resid10_Ca_Cl_PO4Cent.png} \\
  \includegraphics[width=4.0cm]{../Fig/volmap_resid10_Ca_Cl_sn1Cent.png}
  \includegraphics[width=3.6cm]{../Fig/volmap_resid10_Ca_Cl_sn2Cent.png}
  \caption{\label{fig:volmaps}
      Contours of probability isodensities of \ce{Ca2+} with respect to 
      various moieties fixed in space (highlighted with transparent spheres): 
      phosphate moiety, side chain 1 carbonyl group and side chain 2 carbonyl group.
      Shown contours suggest that the dominant contribution 
      to \ce{Ca2+} binding likely comes from the phosphate group, 
      but remain inconclusive on the details of the interactions with any of the two carbonyl groups. 
  }
  \todo{JOE: I'll update this figure with some ensemble of configuration to support binding preference of \ce{Ca2+}}
\end{figure}
